---
title: "Rush Ranch Update 21/10/19"
output: ioslides_presentation
---

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(lubridate)
library(plotly)
data <- read.csv("~/Documents/MS_Thesis/Rush_Ranch/USSrr_v2.csv") %>%
  mutate(date = as.POSIXct(strptime(paste(year, DOY, paste(floor(time), round((time-floor(time))*60),                               sep=":")), format="%Y %j %H:%M")),
         DOY2 = if_else(DOY >= 91, DOY - 90, DOY + 275),
         DOY2 = c(lead(DOY2)),
         Month = month(date))

data$Year2[data$Month < 04 & data$year == 2014] <- "2013-2014"
data$Year2[data$Month >= 04 & data$year == 2014] <- "2014-2015"
data$Year2[data$Month < 04 & data$year == 2015] <- "2014-2015"
data$Year2[data$Month >= 04 & data$year == 2015] <- "2015-2016"
data$Year2[data$Month < 04 & data$year == 2016] <- "2015-2016"
data$Year2[data$Month >= 04 & data$year == 2016] <- "2016-2017"
data$Year2[data$Month < 04 & data$year == 2017] <- "2016-2017"
data$Year2[data$Month >= 04 & data$year == 2017] <- "2017-2018"
data$Year2[data$Month < 04 & data$year == 2018] <- "2017-2018"
data$Year2[data$Month >= 04 & data$year == 2018] <- "2018-2019"

```

# Environmental Variables

## Rainfall

```{r, echo = F}
plot_ly(data, x = ~date, y = ~mm, type = 'bar')
```

## Salinity

```{r, echo = F}
plot_ly(data, x = ~date, y = ~Sal, type = 'scatter', mode = "line")
```

## Air temp

```{r, echo = F}
plot_ly(data, x = ~date, y = ~TA, type = 'scatter', mode = "lines")
```

## Water Table

```{r, echo = F}
plot_ly(data, x = ~date, y = ~Depth, type = 'scatter', mode = "lines")
```

## NDVI

```{r, echo = F}
plot_ly(data, x = ~date, y = ~NDVI_camera, type = 'scatter', mode = "lines")
```

## pH

```{r, echo = F}
plot_ly(data, x = ~date, y = ~pH, type = 'scatter', mode = "lines")
```

## Soil Water Content

```{r, echo = F}
plot_ly(data, x = ~date, y = ~SWC, type = 'scatter', mode = "lines")
```

# Preliminary Dataset: Comparison by Paritioning Technique

## Cumulative NEE

```{r, echo = F}
data %>%
  group_by(Year2) %>%
  mutate(ANN_NEE = er_ANNnight + gpp_ANNnight,
         Reich_NEE = er_Reichstein + gpp_Reichstein,
         linear_NEE = er_linear + gpp_linear,
         ANN = cumsum(ANN_NEE),
         Reich = cumsum(Reich_NEE),
         linear = cumsum(linear_NEE)) %>%
  select(ANN, Reich, linear, Year2, DOY2) %>%
  pivot_longer(cols = c(ANN, Reich, linear),
               names_to = "Method",
               values_to = "cum_NEE") %>%
  drop_na() %>%
  filter(DOY2 > 1,
         Year2 != "2013-2014") %>%
  ggplot(aes(x = DOY2, y = cum_NEE, color = Year2)) +
  facet_wrap(~Method) +
  ylab("Cumulative NEE( µmol CO2 m-2 s-1)") +
  xlab("Days since April 1st") +
  geom_line() +
  theme_bw()
```

## Cumulative ER

```{r, echo = F}
data %>%
  group_by(Year2) %>%
  mutate(ANN = cumsum(er_ANNnight),
         Reich = cumsum(er_Reichstein),
         linear = cumsum(er_ANNnight)) %>%
  select(ANN, Reich, linear, Year2, DOY2) %>%
  pivot_longer(cols = c(ANN, Reich, linear),
               names_to = "Method",
               values_to = "cum_ER") %>%
  drop_na() %>%
  filter(DOY2 > 1,
         Year2 != "2013-2014") %>%
  ggplot(aes(x = DOY2, y = cum_ER, color = Year2)) +
  facet_wrap(~Method) +
  ylab("Cumulative ER( µmol CO2 m-2 s-1)") +
  xlab("Days since April 1st") +
  geom_line() +
  theme_bw()
```

## Cumulative GPP

```{r, echo = F}
data %>%
  group_by(Year2) %>%
  mutate(ANN = cumsum(gpp_ANNnight),
         Reich = cumsum(gpp_Reichstein),
         linear = cumsum(gpp_ANNnight)) %>%
  select(ANN, Reich, linear, Year2, DOY2) %>%
  pivot_longer(cols = c(ANN, Reich, linear),
               names_to = "Method",
               values_to = "cum_GPP") %>%
  drop_na() %>%
  filter(DOY2 > 1,
         Year2 != "2013-2014") %>%
  ggplot(aes(x = DOY2, y = cum_GPP, color = Year2)) +
  facet_wrap(~Method) +
  ylab("Cumulative GPP ( µmol CO2 m-2 s-1)") +
  xlab("Days since April 1st") +
  geom_line() +
  theme_bw()
```

# ReddyProc Output

## Comparison by Flux and Partitioning Method

```{r, echo = F}
data <- read.table("~/Documents/MS_Thesis/Rush_Ranch/REddyResults_RushRanch_20191007_31248140/output.txt",
                   header=T) %>%
        filter(Hour != "-") %>%
        mutate(
          Hour = as.numeric(as.character(Hour)),
          date = as.POSIXct(strptime(paste(Year, DoY, paste(floor(Hour), round((Hour-floor(Hour))*60),                               sep=":")), format="%Y %j %H:%M")),
          DoY = as.numeric(as.character(DoY)),
          DOY2 = if_else(DoY >= 91, DoY - 90, DoY + 275),
          DOY2 = c(lead(DOY2)),
          Month = month(date),
          Year =  as.numeric(as.character(Year)),
          GPP_f = as.numeric(as.character(GPP_f)),
          GPP_DT = as.numeric(as.character(GPP_DT)),
          Reco = as.numeric(as.character(Reco)),
          Reco_DT = as.numeric(as.character(Reco_DT))
         )

data$Year2[data$Month < 04 & data$Year == 2014] <- "2013-2014"
data$Year2[data$Month >= 04 & data$Year == 2014] <- "2014-2015"
data$Year2[data$Month < 04 & data$Year == 2015] <- "2014-2015"
data$Year2[data$Month >= 04 & data$Year == 2015] <- "2015-2016"
data$Year2[data$Month < 04 & data$Year == 2016] <- "2015-2016"
data$Year2[data$Month >= 04 & data$Year == 2016] <- "2016-2017"
data$Year2[data$Month < 04 & data$Year == 2017] <- "2016-2017"
data$Year2[data$Month >= 04 & data$Year == 2017] <- "2017-2018"
data$Year2[data$Month < 04 & data$Year == 2018] <- "2017-2018"
data$Year2[data$Month >= 04 & data$Year == 2018] <- "2018-2019"

data2 <- read.csv("~/Documents/MS_Thesis/Rush_Ranch/USSrr_v2.csv") %>%
  mutate(date = as.POSIXct(strptime(paste(year, DOY, paste(floor(time), round((time-floor(time))*60),                               sep=":")), format="%Y %j %H:%M")))

data %>%
  left_join(data2[, c('date','gpp_ANNnight','er_ANNnight')], by = 'date') %>%
  group_by(Year2) %>%
  mutate(GPP_Nighttime = cumsum(-as.numeric(as.character(GPP_f))*1800*12.01e-6),
         GPP_Daytime = cumsum(-as.numeric(as.character(GPP_DT))*1800*12.01e-6),
         GPP_ANN = cumsum(as.numeric(as.character(gpp_ANNnight))*1800*12.01e-6),
         Reco_Nighttime = cumsum(as.numeric(as.character(Reco))*1800*12.01e-6),
         Reco_Daytime = cumsum(as.numeric(as.character(Reco_DT))*1800*12.01e-6),
         Reco_ANN = cumsum(as.numeric(as.character(er_ANNnight))*1800*12.01e-6)
         ) %>%
  select(GPP_Nighttime, GPP_Daytime, GPP_ANN, Reco_Nighttime, Reco_Daytime, Reco_ANN, Year2, DOY2) %>%
  pivot_longer(cols = -c(Year2, DOY2),
               names_to = c("Flux", "Method"),
               names_sep = c("_"),
               values_to = "cum_value") %>%
  mutate(cum_value = as.numeric(as.character(cum_value))) %>%
  drop_na() %>%
  filter(DOY2 > 1,
         Year2 != "2013-2014") %>%
  ggplot(aes(x = DOY2, y = cum_value, color = Year2, linetype = Flux)) +
  facet_wrap(~Method) +
  ylab("Cumulative Flux (g C m-2)") +
  xlab("Days since April 1st") +
  geom_line() +
  theme_bw() 
```

## Next steps

Comparison of growing season interannual variability
  * *Wavelet Decomposition* ("wavelets" package?)
    * ID biophysical drivers of CO2 + CH4
  * *Information Theory* ("infotheo" package?)
    * ID interaction between salinity and biophys drivers affect on CO2
  * Empirically model CO2: how important is salinity?
  * If salinity is important, what drives salinity?


